Plots for Latent Hawkes Paper

### 2020-07-16 output_scripts/Paper_Plots.Rmd
try other cohort
fix merge conflict. some issues here with the data for some cohorts in fig 10a

current_cohort <- 3

@@

# ------------------- period
training_end <- nrow(df[df$day<=18,])
testing_end <- nrow(df)#1077 #929 for cohort 5
newx <- c(training_end:testing_end)

>>>>

current_cohort <- 1

@@

# ------------------- period
training_end <- nrow(df[df$day<=18,])
testing_end <- nrow(df)-1#1077 #929 for cohort 5
newx <- c(training_end:testing_end)
